Supplemental Information B: Full Annotated Analysis and Reproducible Code

### 2022-01-16 Methods-and-Results.Rmd
descr tables wide
table link fixed

The full surveys are available in our Online Supplementary Material A and the full data description is available in Online Supplementary Materials B. Correlations and descriptive statistics of the included variables are available in Table \ref{tab:descrFullLong} and Table \ref{tab:descrOutLong}.

@@

The full surveys are available in our Online Supplementary Material A and the full data description is available in Online Supplementary Materials B. Correlations and descriptive statistics of the included variables are available in Tables \ref{tab:descrFullLong} and \ref{tab:descrOutLong}.

@@

<!-- \input{Tables/descrFullWide} -->
<!-- \input{Tables/descrOutWide} -->

\input{Tables/descrFullLong}
\input{Tables/descrOutLong}

>>>>

The full surveys are available in our Online Supplementary Material A and the full data description is available in Online Supplementary Materials B. Correlations and descriptive statistics of the included variables are available in Table \ref{tab:descrFullWide} and Table \ref{tab:descrOutWide}.

@@

The full surveys are available in our Online Supplementary Material A and the full data description is available in Online Supplementary Materials B. Correlations and descriptive statistics of the included variables are available in Tables \ref{tab:descrFullWide} and \ref{tab:descrOutWide}.

@@

\input{Tables/descrFullWide}
\input{Tables/descrOutWide}

<!-- \input{Tables/descrFullLong} -->
<!-- \input{Tables/descrOutLong} -->
